Bringing the Power of eBPF to Open vSwitch

### 2018-10-26 paper.tex
Edit 4.4.5

\subsubsection{Summary}
Through the step-by-step analysis, the key to performance is to keep
the process CPU time in userspace, and making sure the userspace process
is dedicated to do packet processing. Moreover, standard optmization
techniques such as batching is critical. Here we apply batching in a
couple of places such as issuing sendmsg syscall, packet reception and
transmission. In summary, OVS-AFXDP shows performance below:
\begin{table}
\centering
\small
\begin{tabular}{|c | c | c|}
\hline
 {\bf Projects} & {\bf xdpsock } & {\bf OVS-AFXDP} \\ \hline\hline
  rxdrop & 19Mpps & 19Mpps \\ \hline
  l2fwd  & 17Mpps & 14Mpps \\ \hline
  \end{tabular}
\caption{\footnotesize
Performance comparison of the xdpsock and and OVS-AFXDP.
}
\label{compare}
\end{table}

>>>>

\subsubsection{Summary}
We summarize the OVS-AFXDP in Table~\ref{compare}.
Through the step-by-step analysis, the keys to performance improvement are to
keep packet processing in userspace to avoid kernel userspace context switch,
and allocating dedicated userspace processes for packet processing.
Moreover, standard optimization techniques such as batching is critical
to performance. We observe performance boost when apply batching to a couple
of places such as issuing sendmsg syscall, packet reception and transmission.
\begin{table}
\centering
\small
\begin{tabular}{|c | c | c|}
\hline
 {\bf Projects} & {\bf xdpsock } & {\bf OVS-AFXDP} \\ \hline\hline
  rxdrop & 19Mpps & 19Mpps \\ \hline
  l2fwd  & 17Mpps & 14Mpps \\ \hline
  \end{tabular}
\caption{\footnotesize
Performance comparison of the xdpsock and OVS-AFXDP.
}
\label{compare}
\end{table}
